An Information Lens on Demographic Diversity

### 2016-11-10 revision.tex
cleaning up

	\subsection{Illustrations}
		\subsubsection{Comparative Analysis: Detroit and Philadelphia}
			To illustrate these methods, we use them to compare the cities of Philadelphia and Detroit. Our data is blockgroup-level demographics from the American Community Survey \cite{CensusRace}. As we show, computing $H(Y)$, $I(X,Y)$, and $J(X,Y)$ together highlights similarities and differences between these cities. 
			\todo{We need to generate a nice summary plot here and then fill this section in.}
			\begin{figure}
				\includegraphics[width = .5\textwidth]{figs/Detroit_percent_black.pdf}
				\includegraphics[width = .5\textwidth]{figs/Detroit_grid.pdf} \\
				\includegraphics[width = .5\textwidth]{figs/Philadelphia_percent_black.pdf}
				\includegraphics[width = .5\textwidth]{figs/Philadelphia_grid.pdf} \\

@@

		\subsubsection{Comparative Diversity Profiles}
			\todo{Is there a fun way to explore the density point? E.g. figure out people per ``neighborhood'' in some way? Think about what I would want the analysis here to be.}

@@

\section{Discussion} \label{sec:discussion}

\bibliography{/Users/phil/bibs/library.bib}{}
\bibliographystyle{plain}

>>>>

	\subsection{Illustrations}
		% \subsubsection{Comparative Analysis: Detroit and Philadelphia}
			To illustrate these methods, we use them to compare the cities of Philadelphia and Detroit. Our data is blockgroup-level demographics from the American Community Survey \cite{CensusRace}. As we show, computing $H(Y)$, $I(X,Y)$, and $J(X,Y)$ together highlights similarities and differences between these cities. 
			% \todo{We need to generate a nice summary plot here and then fill this section in.}
			\begin{figure}
				\includegraphics[width = .5\textwidth]{figs/Detroit_percent_black.pdf}
				\includegraphics[width = .5\textwidth]{figs/Detroit_grid.pdf} \\
				\includegraphics[width = .5\textwidth]{figs/Philadelphia_percent_black.pdf}
				\includegraphics[width = .5\textwidth]{figs/Philadelphia_grid.pdf} \\

@@

		% \subsubsection{Comparative Diversity Profiles}
			% \todo{Is there a fun way to explore the density point? E.g. figure out people per ``neighborhood'' in some way? Think about what I would want the analysis here to be.}

@@

\section{Discussion} \label{sec:discussion}
BLAH BLAH BLAH
% \bibliography{/Users/phil/bibs/library.bib}{}
% \bibliographystyle{plain}
